$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-06 paper/paper.tex
Use \qedhere on proofs ending in itemize
Make the diagrams slightly smaller
on SR

\begin{nidefinition}
  For convenience, we use $\containsusage{\Gamma}{i}{x}{\Delta}$ to stand for $\contains{\gamma}{\Gamma}{i}{t}{x}{\Delta}$ for some $\gamma$ and $t$.
\end{nidefinition}

\begin{nitheorem}[Subject reduction]
  If $P$ reduces to $Q$ and $P$ is well-typed, then so is $Q$.
  In the \picalc{} we distinguish between a reduction $P \reduce{\constr{internal}} Q$ on a channel internal to $P$, and a reduction $P \reduce{\constr{external} \; i} Q$ on a channel $i$ external to $P$.
  Let $P$ be a well-typed process in $\types{\gamma}{\Gamma}{P}{\Xi}$.
  \begin{itemize}
    \item If the reduction is internal, we prove $\types{\gamma}{\Gamma}{Q}{\Xi}$.
    \item If the reduction is external and on channel $i$, we prove that if $\containsusage{\Gamma}{i}{\lio}{\Delta}$ , then $\types{\gamma}{\Delta}{Q}{\Xi}$.
  \end{itemize}
\end{nitheorem}

\begin{proof}
  By induction on $\types{\gamma}{\Gamma}{P}{\Xi}$.
  \hfill{}\\
  \begin{itemize}
    \item
    In the $\constr{comm}$ case we apply framing (\autoref{thm:framing}) to rearrange the assumptions and then apply substitution (\autoref{thm:substitution}) and strengthening (\autoref{thm:strengthening}).

    \item
    Reduction under $\constr{par}$ proceeds by induction on the process that is being reduced.

    \item
    Reduction under scope restriction case splits on the channel $c$ on which communication occurs.
    If $c$ is $\constr{internal}$ we proceed inductively.
    If $c$ is $\constr{external}\; \constr{0}$ -- i.e. the channel that is being introduced by the scope restriction -- we use \autoref{lm:comm-capable} to subtract $\lio$ from the channel's usage annotation and proceed inductively.
    If $c$ is $\constr{external}\; (\suc i)$ we proceed inductively.

    \item
    In the $\constr{struct}$ case, we apply subject congruence (\autoref{thm:subject-congruence}) and proceed inductively.
  \end{itemize}
\end{proof}

>>>>

\begin{note}
  We use $\containsusage{\Gamma}{i}{x}{\Delta}$ to stand for $\contains{\gamma}{\Gamma}{i}{t}{x}{\Delta}$ for some $\gamma$ and $t$.
\end{note}
\todo{use of well-typed:
is well-typed replace with is well typed.
A well-typed P is ok.}
Subject reduction states that if $P$ is well typed and it reduces to $Q$, then $Q$ is well typed.
In the \picalc{} we distinguish between a reduction $P \reduce{\constr{internal}} Q$ on a channel internal to $P$, and a reduction $P \reduce{\constr{external} \; i} Q$ on a channel $i$ external to $P$ (refer to \autoref{operational-semantics}).
\begin{nitheorem}[Subject reduction]
  Let $P$ be a well-typed process in $\types{\gamma}{\Gamma}{P}{\Xi}$
  \begin{itemize}
    \item If $P \reduce{\constr{internal}} Q$, then $\types{\gamma}{\Gamma}{Q}{\Xi}$.
    \item If $P \reduce{\constr{external} \; i} Q$ and $\containsusage{\Gamma}{i}{\lio}{\Delta}$, then $\types{\gamma}{\Delta}{Q}{\Xi}$.
  \end{itemize}
\end{nitheorem}

\begin{proof}
  By induction on $\types{\gamma}{\Gamma}{P}{\Xi}$.
  \hfill{}\\
  \begin{itemize}
    \item
    Case $\constr{comm}$: we apply framing (\autoref{thm:framing}) to rearrange the assumptions and then apply substitution (\autoref{thm:substitution}) and strengthening (\autoref{thm:strengthening}).

    \item
    Case $\constr{par}$: by induction on the process that is being reduced.

    \item
    Case $\constr{res}$: reduction under scope restriction case splits on the channel $c$ on which communication occurs.
    If $c$ is $\constr{internal}$ we proceed inductively.
    If $c$ is $\constr{external}\; \constr{0}$ -- i.e. the channel that is being introduced by the scope restriction -- we use \autoref{lm:comm-capable} to subtract $\lio$ from the channel's usage annotation and proceed inductively.
    If $c$ is $\constr{external}\; (\suc i)$ we proceed inductively.

    \item
    Case $\constr{struct}$: we apply subject congruence (\autoref{thm:subject-congruence}) and proceed inductively.
  \end{itemize}
\end{proof}
